Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

These reductions in the amount of agricultural land would then impact the quantity of agricultural goods that could be produced. For example, the 14.6 percent decrease in agrciultural land in East Asia and the 9.0 percent decrease in agrciultural land in Southeast Asia would result in large declines in percentage terms in agricultural production of 5.1 percent and 2.0 percent, respectively (Table 2). Surprisingly, Brazil and the United States, despite the derease in available agricultural land compared to the baseline 2033 scenario, are estimated to see increased agricultural output of 0.2 percent and 0.6 percent, respectively. This may be tied to the sharp declines in other regions prompting greater production for export.

@@

When we examine how this impacts exports of agricultural goods, we find that Japan and the United States appear to be the biggest beneficiaries of this policy with their exports increasing 8.8 percent and 3.5 percent, respectively (table 3). The regions where agricultural exports drop most significantly are East Asia, South Asia, Southeast Asia, and Central America who see decreases of 14.5 percent, 5.9 percent, 5.1 percent,and 5.0 percent, respectively.

@@

Overall, this policy, while creating the positive result of avoiding deforestation, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (table 4). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.

>>>>

These reductions in the amount of agricultural land would then impact the quantity of agricultural goods that could be produced. For example, the 14.6 percent decrease in agrciultural land in East Asia and the 9.0 percent decrease in agrciultural land in Southeast Asia would result in large declines in percentage terms in agricultural production of 5.1 percent and 2.0 percent, respectively (Table 2). Surprisingly, Brazil and the United States, despite their dereases in available agricultural land compared to the baseline 2033 scenario, are estimated to see increased agricultural output of 0.2 percent and 0.6 percent, respectively. This may be tied to the sharp declines in other regions prompting greater intensity of production to satisfy external demand.

@@

When we examine how this impacts exports of agricultural goods, we find that exports from Japan and the United States grow the most, increasing 8.8 percent and 3.5 percent, respectively (table 3). The regions where agricultural exports drop most significantly are East Asia, South Asia, Southeast Asia, and Central America who see decreases of 14.5 percent, 5.9 percent, 5.1 percent,and 5.0 percent, respectively.

@@

Overall, this tax policy, which results in zero net deforestation globally, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (table 4). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.
